### 2023-09-10 README.Rmd
Updated readme
Added author

> Sjölander M., Linderholm, J., Geladi P (2023). _`r Title`_. Journal of Archaeological and Anthropological Sciences <https://doi.org/xxx/xxx>

@@

> Sjölander M., Linderholm, J., Geladi P (2023). _`r Title`_. Journal of Archaeological and Anthropological Sciences `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Sjölander M., Linderholm, J., Geladi P (2023). (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console

>>>>

> Sjölander M., Linderholm, J., Geladi P., Buckland, P. I. (2023). _`r Title`_. (Journal name) <https://doi.org/xxx/xxx>

@@

> Sjölander M., Linderholm, J., Geladi P., Buckland, P. I. (2023). _`r Title`_. (Journal name) `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Sjölander M., Linderholm, J., Geladi P., Buckland, P. I. (2023). (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.pdf`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console
